---
title: "Project 3"
output: 
  html_document:
  theme: cosmo
Author: "Grayson Gayle, Madeline Nash, David Schluckebier"
Date: Due October 16, 2015 11:59 pm
---
  The data used in our project reflects the different attributes for nearly a hundred different plant species. We manipualted this data to visualize the aggregate ratios of these attributes with means and standard deviations.
  
Also, there is a lot of other information within the repository about each of the different plant species.

First, we created a dataframe named djdf for our plant data from the online oracle cloud server using the following code:
  
  ```{r}

require("jsonlite")
require("RCurl")
require("ggplot2")
require("ggthemes")
require("gplots")
require("grid")
require("RCurl")
require("reshape2")
require("rstudio")
require("tableplot")
require("tidyr")
require("dplyr")
require("jsonlite")
require("extrafont")
require("lubridate")
require(tidyr)
require(dplyr)
require(ggplot2)

sha <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from data_sha"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_gmg954', PASS='orcl_gmg954', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))

tex <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from data_tex"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_gmg954', PASS='orcl_gmg954', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))

mar <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from data_mar"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_gmg954', PASS='orcl_gmg954', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))

```


We then used this data to create the following three data wrangling visualizations:
  
  
**Figure 1**
* This data compares the ratio of the margin size of the leaf species to the texture value of the same leaf species.  This graph shows the relationship between different species types and their margin and texture values as shown in the following graph.  This only shows species in which their margin value is 10 times greater than their texture values.  This may be useful to botanists who are curious about the different data relationships that occur in specific plant species.*
```{r}
source("/Users/Grayson/Desktop/DataVisualization/Project 3/02 Data Wrangling/Wrangle1.R", echo = TRUE)
```

**Figure 2**
  *This data compares the ratio of the shape of the leaf species to the texture value of the same leaf species.  Neither of these graphs were able to have an outer join as the only join value of species is always matched to the other two data sets.  This graph shows the relationship between different species types and their shape and texture ratio values as shown in the following graph.  The relationship in this graph shows how close a plants shape is related in value to its texture. This may be useful in finding to what degree a plant specie shape results in a certain texture value.*
```{r}
source("/Users/Grayson/Desktop/DataVisualization/Project 3/02 Data Wrangling/Wrangle2.R", echo = TRUE)
```

**Figure 3**
  *This data compares the standard deviation of the margin to the standard deviation of the shape.  This shows how much compareitively the shape and margin differ within each species as well as among each of the specimen of a particular plant species.  The results are shown below in order from the least deviating ratios to the greatest deviation ratios.  We can see at the upward sloping trend that most plant species differ from margin to shape by about 100 points while the outlier differ about 4 times as much across each of the species.*  
```{r}
source("/Users/Grayson/Desktop/DataVisualization/Project 3/02 Data Wrangling/Wrangle3.R", echo = TRUE)
```